---
title: "STAT 488 Project Report"
author: "Qing Gong, Nathan Lutz, Bao Van"
date: "12/5/2021"
output: 
  html_document:
  code_folding: show
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{css, echo=FALSE}
h1{text-align: center; 
  color:Tomato;
  #font-weight: bold;}
   
h4{text-align:center;
  color:DarkSlateGray}

h5{text-align:left;
  color:SlateBlue;}
```

```{r results='hide', message=FALSE, warning=FALSE}
#Load library
library(tidyverse);library(ggplot2);library(gridExtra);library(rstatix); library(lme4)
#library(lattice);
```

##### Input the primary data   
Creates an environment containing all list components(csv file) as objects and then read all all csv files into R.
```{r}
setwd("/Lectures/S488-002/Project/team/Consulting")
temp = list.files(pattern="*.csv")
list2env(
  lapply(setNames(temp, make.names(gsub("*.csv$", "", temp))), 
         read.csv), envir = .GlobalEnv)
```

##### Data cleaning   
*1*. *user40* was a test case, which needs to be removed   
*2*.Remove extra observation. For each student, they are supposed to do each game once. 
  For each game, every one should have unique start time stamp
  In R5, user6(B6) have two start time stamp for quick tap level 2, 2nd try is deleted here

```{r}
R1 <- round1_updated %>% filter(userid != 'user40')
R5 <- round5_updated %>% filter(level_start_timestamp != "2021-03-25T18:55:58.767Z")
```

*3*. Add treatment information from NeurUX.Intrvention.Group file
extract id number from NeurUX.ID, add A to Id numbers for 2021 Fall or B for Spring 2021 

```{r}
#intervention 1 and control 0
Intervention1 <- read.csv("Consulting/NeurUX.Intervention.Group.csv") %>% 
  slice(2:15) %>% 
  mutate(ID = paste0('B', substr(NeurUX.ID, 5, 7))) %>% 
  select(treatment= Intervention.Group, Study.ID, ID)

Intervention2 <- read.csv("Consulting/NeurUX.Intervention.Group.csv")%>%
  slice(18:36) %>% 
  mutate( ID = paste0('A', substr(NeurUX.ID, 5, 7))) %>% 
  select(treatment= Intervention.Group, Study.ID, ID)

#combine subdata
Intervention <- rbind(Intervention1, Intervention2)
```


*4*. Merge intervention data set into the primary dataset
Add columns time_point 1(round1 and round4), 2(round 2 and round 5), 3(round 3 and round6)
Since subjects in two semester are different userID could be renamed to unique ID 
extract id number from ID, add A to Id numbers for subjects in 1 st semester or B for 2nd semester 

```{r}
R1 <- mutate(R1, time_point = 1, ID = paste0('A', substr(userid, 5, 7)))
R2 <- mutate(round2_updated, time_point = 2, ID = paste0('A', substr(userid, 5, 7)))
R3 <- mutate(round3_updated, time_point = 3, ID = paste0('A', substr(userid, 5, 7)))
R4 <- mutate(round4_updated, time_point = 1, ID = paste0('B', substr(userid, 5, 7)))
R5 <- mutate(R5, time_point = 2, ID = paste0('B', substr(userid, 5, 7)))
R6 <- mutate(round6_updated, time_point = 3, ID = paste0('B', substr(userid, 5, 7)))

#combine all data into one whole dataset
R_all <- rbind(R1, R2, R3, R4, R5, R6)
#view the features of original data
#head(R_all)
#Merge Intervention into R_all dataset
data <- merge(R_all, Intervention, by = "ID")
```

##### Subset color trick data
```{r}
colorTrick <- data %>% select (
  time_point,
  treatment,
  game_name,
  ID, 
  response_reaction_time,
  correct_count,
  Study.ID,
  event_type,
  is_response_correct,
  incorrect_count,
  user_response,
  mechanic_name
) %>%
  filter(game_name %in% c("color trick 1",
                          "color trick 2",
                          "color trick 3"),
         event_type == "trial"
         )
#sum(is.na(colorTrick))
#head(colorTrick)
```

Calculate average reaction time and correct proportion for each subject at each time point for each color and add them into the dataset.
Transform average reaction time by logthrime to make data more normal.

```{r}
colorT <- colorTrick %>% filter(event_type == "trial" &
                                  is_response_correct == TRUE) 
color <- colorT %>% 
  group_by(treatment,game_name, ID, Study.ID, time_point) %>%
  summarise('average_RT' = sprintf("%0.2f", mean(response_reaction_time)),
            'tcorrect'= sum(is_response_correct),
            'prop_ncorrect' = max(correct_count)/sum(max(correct_count) + max(incorrect_count)),
            .groups = 'drop') %>% 
  mutate(across(c(treatment, game_name, time_point, ID), as.factor),
         across(average_RT, as.numeric),
         log_avg_RT=log(average_RT))
```


First peek   
Check average_RT for 3 color trick games and compare plots before and after transformation
```{r}
g1 <- ggplot(color, aes(x = game_name, y = average_RT))  +
  geom_boxplot(fill = rep(c("#bad2d7", "#ffd9df", "#9ec2e2"), length = 3)) +
  theme_classic() 
g2 <- ggplot(color, aes(x = game_name, y = log_avg_RT))  +
  geom_boxplot(fill = rep(c("#bad2d7", "#ffd9df", "#9ec2e2"), length = 3)) +
  theme_classic()
grid.arrange(g1, g2, ncol=2)

#check extreme outliers
# pc %>% 
#   group_by(game_name) %>% 
#   identify_outliers(log_avg_RT)
#No extreme outliers
```

Plots show that color trick 3 requires longer reaction time, which indicates it's harder than other color tricks.

Test average reaction time difference for three color trick games.   
Normality is still not satisfied.Non-parametric test, Kruskal-Wallis test, was employed and small p-value shows significant difference among three color tricks.    
Pair-wise comparison test indicates any two of them has significant different transformed average reaction time.
```{r}
#anova test
m1 <- lm(log_avg_RT ~ game_name, data = color)
anova(m1)
#normality check
shapiro.test(m1$residuals)
# small p-value from Shapiro-Wilk test indicates non-normality

kruskal.test(log_avg_RT ~ game_name, data = color)
pairwise.wilcox.test(color$log_avg_RT, color$game_name)
```

Since reaction time for three color trick games is statistically different, three color trick games would be analyzed separately.

Check average reaction time difference for three time points
```{r}
ggplot(color, aes(x = game_name, y = log_avg_RT)) +
  geom_boxplot(aes(fill = time_point), notch = T, alpha = 0.6) +
  labs(title = "Avgerage reaction time(log) by game and time point", y = "Average reaction        time(log)", x = "Time point") +
  theme_classic()
#"#33ff66","#ffd9df","#9ec2e2"
```

**Extract each color trick subsets from *color* data**

```{r}
ct1 <- color %>% filter(game_name == "color trick 1") %>%
  select(treatment,
         ID,
         time_point,
         average_RT,
         log_avg_RT,
         prop_ncorrect,
         tcorrect)  %>%
  mutate(time_point = factor(time_point))

ct2 <- color %>% filter(game_name == "color trick 2") %>%
  select(treatment,
         ID,
         time_point,
         average_RT,
         log_avg_RT,
         prop_ncorrect,
         tcorrect) %>%
  mutate(time_point = factor(time_point))

ct3 <- color %>% filter(game_name == "color trick 3") %>%
  select(treatment,
         ID,
         time_point,
         average_RT,
         log_avg_RT,
         prop_ncorrect,
         tcorrect)  %>%
  mutate(time_point = factor(time_point))
```

Check average reaction time(log) by treatment at each time point for each color trick

```{r}
ggplot(ct1, aes(time_point, log_avg_RT, fill = treatment)) +
  geom_boxplot(position = position_dodge(0.7),
               width = 0.4,
               alpha = 0.2) +
  geom_dotplot(binaxis = "y",
               stackdir = "center",
               position = position_dodge(0.7),alpha = 0.7, binwidth = 0.034) +
  labs(title = "Color trick 1", y = "Average reaction time(log)", x = "Time point") +
  theme_classic()

ggplot(ct2, aes(time_point, log_avg_RT, fill = treatment)) +
  geom_boxplot(position = position_dodge(0.7),
               width = 0.4,
               alpha = 0.2) +
  geom_dotplot(binaxis = "y",
               stackdir = "center",
               position = position_dodge(0.7), alpha = 0.7, binwidth = 0.0748) +
  labs(title = "Color trick 2", y = "Average reaction time(log)", x = "Time point") +
  theme_classic()

ggplot(ct3, aes(time_point, log_avg_RT, fill = treatment)) +
  geom_boxplot(position = position_dodge(0.7),
               width = 0.4,
               alpha = 0.2) +
  geom_dotplot(binaxis = "y",
               stackdir = "center",
               position = position_dodge(0.7), alpha = 0.7, binwidth = 0.051) +
  labs(title = "Color trick 3", y = "Average reaction time(log)", x = "Time point") +
  theme_classic()

# res.aov <- anova_test(pc3, dv = log_avg_RT, wid=ID, between=treatment, within=time_point)
# get_anova_table(res.aov)
```

Plot 1
For the control group the average reaction time(*log_avg_RT*) decreases from time point 1(T1) to time point 2(T2), slightly increase from time point 2 to time point 3(T3). 
For the intervention group,  *log_avg_RT* barely changes over time. Practice effect may work here, especially from T1 to T2.

Plot 2 
*log_avg_RT* for the intervention group decreases a little and then slightly increases over time.
For the control group, *log_avg_RT* get some reduction. 
Practice effect could be considered there.

"Practice effects occur when a person is exposed to a test or measurement technique."


Plot 3 
For intervention group, *log_avg_RT* slightly drops from T1 to T2, obviously decrease from T2 to T3. 
For the control group, *log_avg_RT* decreases over time.

For T3, the intervention group has longer *log_avg_RT* than the control group for color trick 2 and color trick 3.
Guess this maybe because color trick 2 and color trick 3 are harder than color trick 1. Besides, the period between T2and T3 may be longer than that between T1 and T2.


##### Read in SMILE DATA

```{r}
SMILE <- read.csv("Consulting/SMILE full data 10 23 21_AARThesis_Deidentified_forNL.csv")  #  HS group = 1, Control group = 2

#SMILE$PHQ1_T2R[SMILE$StudyID_T1 == 22585621]   # should we remove this 26 > 25?
#SMILE$PHQ_T1_total[SMILE$StudyID_T1 == 22585602]   # 0 is abnormal?

#change control group = 2 into 0
SMILE$treatment1 <- ifelse(SMILE$Group_HSvsNoHS == 1, 1, 0)

#Check PHQ is from PHQ_TD_total = sum(PHQD_TDR)
# PH <- SMILE %>% 
#   select(StudyID_T1, starts_with("PHQ")) %>% 
#   rename(Study.ID = StudyID_T1)
# PHT <- PH %>% 
#   select(ends_with("_T3R"))   #PHQ_T1_total = sum(PHQD_TDR)
#   
# PHT$TOTAL = apply(PHT, 1, sum)
# PHT$SUM = PH$PHQ_T3_total  

PHQ <- SMILE %>%
  select(
    StudyID_T1,
    Gender_Numeric_T1,
    MotherEdu_T1,
    ParentalHouseholdIncome_T1,
    Grade_T1,
    AgeExact_T1,
    PHQ_T1_total,
    PHQ_T2_total,
    PHQ_T3_total,
    treatment1
  ) %>%
  rename(
    Study.ID = StudyID_T1,
    "1" = PHQ_T1_total,
    "2" = PHQ_T2_total,
    "3" = PHQ_T3_total
  ) %>%
  gather("1", "2", "3", key = time_point, value = "PHQ")       #change wide-format PHQ for 3 time points into long format

#check all intervention participants in smile data at T1
#sum(NeurUX.Intervention.Group$Study.ID %in% SMILE$StudyID_T1)

#combine PHQ and color trick game
pnc <- left_join(color, PHQ, by = c("Study.ID", "time_point"))
```

Check correlation among grade, mother education, household income, average reaction time, PHQ
```{r}
relation <- PHQ %>% mutate(mom_edu = ifelse(MotherEdu_T1 == "Some High School", 1, 
                                       ifelse(MotherEdu_T1 == "High School", 2, 
                                              ifelse(MotherEdu_T1 == "Some College", 3, 
                                                     ifelse(MotherEdu_T1 == "College", 4, 
                                                            ifelse(MotherEdu_T1 == "Graduate School", 5, ""))))),  
                      grade=ifelse(Grade_T1=="First-year", 1, 
                                   ifelse(Grade_T1=="Sophomore", 2, 
                                          ifelse(Grade_T1=="Junior", 3, 
                                                 ifelse(Grade_T1=="Senior", 4,
                                                        ifelse(Grade_T1 == "Other (fee", 4, ""))))),
                      income=ifelse(ParentalHouseholdIncome_T1=="Under $25,000", 1, 
                                    ifelse(ParentalHouseholdIncome_T1=="$25,000-$50,000", 2, 
                                           ifelse(ParentalHouseholdIncome_T1 == "$50,000-$75,000", 3,
                                                  ifelse(ParentalHouseholdIncome_T1 == "$75,000-$100,000", 4, 
                                                         ifelse(ParentalHouseholdIncome_T1 == "$100,000-$150,000", 5,
                                                                ifelse(ParentalHouseholdIncome_T1 == "$150,000-$200,000", 6,
                                                                       ifelse(ParentalHouseholdIncome_T1 == "Over $200,000", 7, ""))))))), 
                      gender = Gender_Numeric_T1)

#combine PHQ and Neuro-ux
PHQ_UX <- left_join(color, relation, by = c("Study.ID", "time_point"))

merg <- PHQ_UX %>% select(average_RT, prop_ncorrect, tcorrect, AgeExact_T1, gender, treatment, PHQ, mom_edu, income, grade, time_point) %>% 
  mutate(across(where(is.character), as.numeric),
         treatment= as.numeric(treatment))

library(corrplot)
m <- cor(merg)
corrplot(m)
# cor(merg$average_RT, merg$PHQ)
# cor(merg$prop_ncorrect, merg$PHQ)

```

##### Correlation plot
Average reaction time(*average_RT*) is negatively related with total number of correct(*tcorrect*) and proportion of correct(*prop_ncorrect*) as we assumed.
Overall, PHQ doesn't obviously correlated with any variables of interest, except gender.
Female(1) tends to have higher PHQ than male. 

We suppose PHQ positively correlated with *average_RT* and negatively correlated with 
*tcorrect* or *prop_ncorrect*. But this plot shows the opposite direction. 

Different color tricks, time point and treatment conditions would be covered in the next step.

Since we assume PHQ is related with *average_RT*, we could perform a MANOVA test to analyze group means based on these two dependent variables.

##### MANOVA TEST
```{r}
#get target dataset
pc3 <- pnc %>% 
      filter(game_name=="color trick 3") %>% 
      select(-AgeExact_T1, -MotherEdu_T1, -ParentalHouseholdIncome_T1, -Grade_T1, -Study.ID, -treatment1) %>% 
      mutate(time_point = as.factor(time_point),
             gender = as.factor(Gender_Numeric_T1))

b1 <- ggplot(pc3, aes(treatment, PHQ, fill=(treatment))) + 
  geom_point(width = 1)+
   geom_boxplot(outlier.shape = NA, size= 0.3)+
  theme(legend.position = "top")

b2 <- ggplot(pc3, aes(treatment, log_avg_RT, fill=(treatment))) + 
  geom_point()+
  geom_boxplot(outlier.shape = NA, size = 0.3)+
  theme(legend.position = "top")

grid.arrange(b1,b2, ncol=2)

#MANOVA
#differences among treatment groups by considering average reaction time and log_avg_RT

#summary statistics for dependent variables log(averag)
# pc3 %>% group_by(treatment) %>% summarise(mean=mean(PHQ), sd=sd(PHQ))
# 
# pc3 %>% group_by(treatment) %>% summarise(mean=mean(log_avg_RT), sd=sd(log_avg_RT))

#peform one-way manova
dep_vars <- cbind(pc3$PHQ, pc3$log_avg_RT)
fit <- manova(dep_vars ~ treatment, data=pc3)
summary(fit)
```
P-value = 0.2791 indicates that treatment doesn't have a statistically significant association with both combined average reaction time and PHQ.

**Assumptions check**

```{r}
#univariate normality for each combination of the independent and dependent variables

#pc3 %>% group_by(treatment) %>% shapiro_test(PHQ, log_avg_RT)
#data follows univariate normality.

#or check multivariate normality using Mardia’s Skewness and Kurtosis test
library(mvnormalTest)
mardia(pc3[, c("PHQ", "log_avg_RT")])$mv.test
```

Mardia’s Skewness and Kurtosis test, we fail to reject the null hypothesis and conclude that data follows multivariate normality.

*Check Homogeneity of the variance-covariance matrices*
```{r}
library(heplots)
boxM(Y = pc3[, c("PHQ", "log_avg_RT")], group= pc3$treatment)
```

A big p-value shows variance-covariance matrices are equal for each combination of dependent variables formed by each treatment group

*Multivariate outliers*
```{r}
library(rstatix)
mahalanobis_distance(data= pc3[, c("PHQ", "log_avg_RT")])$is.outlier
```

No outliers shown here.

*Linearity assumption*
```{r}
pl0 <- pc3 %>% group_by(treatment) %>% filter(treatment == "0") %>% ggplot(aes(x=log_avg_RT, y= PHQ)) + geom_point() + geom_smooth(method ="lm") + ggtitle("treatment 0")
pl1 <- pc3 %>% group_by(treatment) %>% filter(treatment == "1") %>% ggplot(aes(x=log_avg_RT, y= PHQ)) + geom_point() + geom_smooth(method = "lm")+ ggtitle("treatment 1")
grid.arrange(pl0, pl1)
```

Plots show average reaction time has a linear relationship with PHQ for each group in the treament variable.

*Multicollinearity assumption*
```{r}
cor(x = pc3$PHQ, y = pc3$log_avg_RT)
```

The correlation is weak, separate univariate ANOVA could be performed here.
Since our data is unbalanced, we could use a multi-level linear model to analyze whether treatment and time points have statistical effect on average reaction time.

##### Multi-level linear models  
1. unbalanced data   
2. avoid sphericity issues     
sphericity is equality of variance of the differences between all possible pairs of within-subject conditions
```{r}
#Run multi-level linear model for color trick 1
lme1 <- lmer(log_avg_RT~ 1 + (1|ID), data = pc3)
lme2 <- update(lme1, .~. + treatment)
lme3 <- update(lme2, .~. + time_point)
Anova(lme3)
lme4 <- update(lme3, .~. + treatment*time_point) # interaction is insig.
anova(lme1, lme2, lme3, lme4)
```
Assumption check 
```{r}
#assumption check
plot(lme3)
qqnorm(resid(lme3))
shapiro.test(resid(lme3))

# assumption verified 
# interaction insignificant. choose model 3, from Anova table, both treatment and time_point insig.
```


The output show for color trick 3, average reaction time is significantly different at 3 time points and that there is no difference between control group and intervention group. 
We may conclude that for hard game one could have short average reaction time after practice but treatment doesn't help reduce average reaction time.

Perhaps longer time period and balanced data could works better for treatment effect.

**References**:

 https://www.reneshbedre.com/blog/manova.html          
 https://jackauty.com/multi-level-linear-model/       
 https://www.psywww.com/intropsych/ch01-psychology-and-science/operational-definitions.html#practiceeffects*
